Change in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2019-12-05 analysis/paper/paper.Rmd
added definitions

--->

@@

The research analyzes total 33 assemblages [need to explain what is the difference between 'assemblage' and 'site'] and they consist of cores, blade cores, blades, flakes, debris, hammers, choppers, plans, polyhedrals, side scrapers, end scrapers, notches, cleavers, stemmed points, awls, denticulates, burins, handaxes, blanks, knives, handadzes, peaks, flatters, flakers etc,

>>>>

-->

@@

The research analyzes total 33 assemblages [need to explain what is the difference between 'assemblage' and 'site'] and they consist of cores, blade cores, blades, flakes, debris, hammers, choppers, plans, polyhedrals, side scrapers, end scrapers, notches, cleavers, stemmed points, awls, denticulates, burins, handaxes, blanks, knives, handadzes, peaks, flatters, flakers etc.

<!-- GP needs to explain what is the difference between 'assemblage' and 'site', need to be very precise about the definitions of these: ‘assemblage’ and ‘layer’. Don’t say ‘layer’ at all, say ‘excavation unit’ or ‘stratigraphic unit’. Add a short example of how you identify multiple assemblages in one site (one sentence). => I don't know how to put these definitions in the manuscript naturally.

- Assemblage is a set of artifacts that are found in same exacation unit so archaeologists assume that they are associated each other in terms of period and used by same group of people (GP).

- Assemblage is a group of artifacts recurring together at a particular time and place, and representing the sum of human activities (Renfrew and Bahn 1996).

- Site is a place where past activity is preserved with material evidence.

- This research analyzes total 33 assemblages from 22 sites. Some sites have mutiple  assemblages from differnt stratigraphic units.

-->
